---
title: "`r Sys.getenv('PROJ_TITLE')`"
subtitle: 0.0.0.9000
description: "First-exploration report"
author:
  - name: Corrado Lanera
    url: https://CorradoLanera.it
    orcid_id: "0000-0002-0520-7428"
    affiliation: Unit of Biostatistics, Epidemiology, and Public Health
    affiliation_url: https://www.unipd-ubep.it/
  - name: Silvano Salaris
    orcid_id: "0000-0002-8389-7460"
    affiliation: Unit of Biostatistics, Epidemiology, and Public Health
    affiliation_url: https://www.unipd-ubep.it/
  - name: Giulia Lorenzoni
    orcid_id: "0000-0003-1771-4686"
    affiliation: Unit of Biostatistics, Epidemiology, and Public Health
    affiliation_url: https://www.unipd-ubep.it/
  - name: Danila Azzolina
    orcid_id: "0000-0002-8185-5742"
    affiliation: Unit of Biostatistics, Epidemiology, and Public Health
    affiliation_url: https://www.unipd-ubep.it/
  - name: Dario Gregori
    orcid_id: "0000-0001-7906-0580"
    affiliation: Unit of Biostatistics, Epidemiology, and Public Health
    affiliation_url: https://www.unipd-ubep.it/
citation_url: "`r Sys.getenv('PROJ_URL')`"
date: "`r Sys.Date()`"
bibliography: packages.bib
link-citations: true
preview: man/img/LAIMS.png
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
---

<!-- DON'T RENDER THE REPORT BY HAND DIRECTLY! -->
<!-- use `targets::tar_make()` instead -->


```{r setup, include=FALSE}
options(
  width = 90,
  tidyverse.quiet = TRUE
)

knitr::opts_chunk$set(
  echo = FALSE,
  collapse = TRUE,
  comment = ""
)

library(glue)
library(here)
library(targets)
library(tidyverse)

list.files(here("R"), pattern = "\\.R$", full.names = TRUE) |>
  lapply(source) |> invisible()
```


```{r, message=FALSE}
htmltools::img(
 src = knitr::image_uri(here("man", "img", "LAIMS.png")),
 alt = 'logo',
 style = 'position:absolute; top:0; right:0; padding:10px;'
 )
```


```{r packages, include=FALSE}
library(DT)
```

## Introduction

Weanings data are stored in two main types of files:

<aside>
Data types are three: there are REG files also.
See section **Discussion** for more details.
</aside>

- TRD, reporting ventilators signals averaged every minute.
- LOG, reporting alarms and additional information from the ventilators

TRD and LOG files are collected in pairs, reporting data from
approximately 24 hours each pair. So, every patient have multiple pairs
of TRD and LOG files. Pairs from all the patient of a center involved 
in the study are collected in a folder named with the center code. An
additional __mother__ folder contains all the center's folders.


## Methods


The pipeline developed is currently in the following state

<aside>
The pipeline itself, derived objects, and the report are automatically
monitored for outdated nodes, and updated at any change in the code or
data.
</aside>

```{r}
out <- capture.output({
  net <- tar_visnetwork(
  # targets_only = TRUE,
  exclude = c(
      "report",
      all_of(extract_fct_names(here::here("R/utils.R"))),
      matches("^\\..*$")
    )
  )  
})

net

```



## Results



```{r, echo=FALSE}
weanings_trd <- tar_read(weaningsTRD)
problematic_dupes <- tar_read(problematicDupes)

weanings_log <- tar_read(weaningsLOG)

```


### TRD

- The merged TRD dataset has `r nrow(weanings_trd)` rows, and
`r ncol(weanings_trd)` columns.

Here below a sample of 50 (random) records.

```{r, layout="l-body-outset"}
weanings_trd |>
  dplyr::slice_sample(n = 50) |> 
  datatable(filter = "top", options = list(scrollX = TRUE))
```



### LOG


- The merged LOG dataset has `r nrow(weanings_log)` rows, and
`r ncol(weanings_log)` columns.

Here below a sample of 50 (random) records.

```{r, layout="l-body-outset"}
dplyr::slice_sample(weanings_log, n = 50) |> 
  datatable(filter = "top", options = list(scrollX = TRUE))
```


## Preliminar analyses

### Descriptives

```{r}
paz <- weanings_trd |> 
  select(folder, id_pat) |> 
  distinct() |> 
  group_by(folder) |> 
  summarise(`Numero pazienti` = n()) |> 
  arrange(desc(`Numero pazienti`)) |> 
  rename(Centro = folder)

paz |> 
  datatable(filter = "top", options = list(scrollX = TRUE))
```

<aside>
All'interno dei dati importati sono presenti `r sum(paz[["Numero
pazienti"]])` pazienti totali.
</aside>


```{r, layout="l-body-outset"}
tar_read(ggPatPerCentro)
```


```{r, layout="l-body-outset"}
tar_read(ggDistAllarmi)
```

```{r, layout="l-body-outset"}
tar_read(ggMissingTRD)
```



## Discussion

### Issues

- some lines of signals have wrong time and they results in duplicated
records. This issue involves the following records

```{r, layout="l-body-outset"}
problematic_dupes |> 
  datatable(filter = "top", options = list(scrollX = TRUE))
```


- File in the `VC/` folder are the only one using ISO format for dates.
We have managed that correctly to consistently merge them with the other files.


- In alcuni file LOG (es: `AN004_869`) il nome del paziente non è
riportato come codifica ma esplicitamente. Gli id dei pazienti sono
stata importanti sempre recuperandoli dal nome del file.

<aside>
Nell'intestazione dei file compare sia "nome paziente" che "id
paziente", il primo ogni tanto ha il nome esplicito ogni tanto l'id. A
volte uno dei due manca.
</aside>

### Questions

- There are **REG** files inside the folders which are not reported as
used in the thesis or in the Python importing script. Do they need to be
used? (How?) They seams to have live data (without explicit time) of
the following form:

```
Fase respiro	Pressione	Flusso	Volume			Trigger
Fase	cmH₂O	l/min	ml			
```



## Acknowledgments {.appendix}

For the Weaning project, we have setup an automated environment
tracking changes and updates within the defined pipeline (from import,
preprocess, analyses, and reporting) [@R-targets].


Data are imported using functions from the `{tidyverse}` suite
of R packages mainly [@R-tidyverse].



## Environment {.appendix}

<details>
  <summary>Session info</summary>
```{r, results='markup'}
devtools::session_info()
```
</details>

```{r}
c("tidyverse", "targets") |> 
  knitr::write_bib(here("reports/packages.bib"))
```

